Diffantom: a whole-brain diffusion MRI phantom derived from a real dataset

### 2015-08-12 paper/main.tex
Fixing figure 2, #37
refactoring figure 2, close #37

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\linewidth]{figures/figure02}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:figure2} Figure \arabic{figure}. }%
{\textbf{A. Recommended use of \emph{Diffantom}}.
The dataset can be used to test algorithms and pipelines against a perturbation that is
  introduced in \emph{Diffantom}.
Perturbations can model typical artifacts found in \gls*{dmri} datasets or pathological conditions
  such as a tumor.
\textbf{B1. Tractogram of fibers crossing slice 56 of \emph{Diffantom}} as extracted with \emph{MRTrix},
  represented over that corresponding slice of the \emph{b0} volume.
\textbf{B2. Segmentation of some fiber bundles using \emph{tract\_querier}}: the right \gls*{cst} is
  represented in blue color, the left \gls*{cst} in red, and the forceps minor in green.
  The box includes the slice 56 of the \emph{b0} and the pial surface is represented with transparency.
}
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
\includestandalone[width=\linewidth]{figure02}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:figure2} Figure \arabic{figure}. }%
{\textbf{A. Recommended use of \emph{Diffantom}}.
The phantom is designed to be used as ground-truth information in evaluation frameworks,
  to implement unit test of algorithms, to check integration of processing units within
  pipelines or to validate complete workflows.
For instance, in order to evaluate artifacts, a perturbation can be induced in the microstructural
  model or after simulation to provide reference and test datasets.
\textbf{B1. Tractogram of fibers crossing slice 56 of \emph{Diffantom}} as extracted with \emph{MRTrix},
  represented over that corresponding slice of the \emph{b0} volume.
\textbf{B2. Segmentation of some fiber bundles using \emph{tract\_querier}}: the right \gls*{cst} is
  represented in blue color, the left \gls*{cst} in red, and the forceps minor in green.
  The box includes the slice 56 of the \emph{b0} and the pial surface is represented with transparency.
}
\end{figure}
